Real-time Thrust Estimation and Regulation for Multirotor Aerial Vehicle\\ {} \thanks{}

### 2018-09-16 paper/drafts/IEEE_VERSION.tex
bara look at IEEE_VERSION

\documentclass[conference]{IEEEtran}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\graphicspath{images}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Paper Title*\\
	{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
		should not be used}
	\thanks{Identify applicable funding agency here. If none, delete this.}

@@

\author{\IEEEauthorblockN{1\textsuperscript{st} Adithya Ravishankara}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	\and
	\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
	\IEEEauthorblockA{\textit{dept. namefdsfsdf of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	\and
	\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
	\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
		\textit{name of organization (of Aff.)}\\
		City, Country \\
		email address}
	\section{Intro}
	\subsection{Intro to mav and control system architecture}
	Multirotor Aerial Vehicles (MAV), specifically quadrotors, have become quite commonplace in many industries ranging from filmography to racing to even military operations. Over the past decade, there has been an incredible amount of research and advancement within this field leading to its proliferation and allowing for the technology to become more accessible. One of the major areas of research regarding MAV's is the control system that directs the motor-rotor system. The control mechanism ranges in complexity from the common motor-rotor control, to a more complex system that takes into consideration parameters such as thrust or torque. The control of the motor-rotor has to account for multiple different external and internal factors, from the ambient wind speed, the rotation speed of the propeller (RPM), the pitch of the propeller, and for more complex controllers, the internal loops of the Electronic Speed Controller (ESC) or Flight Controller (FC). \\
	In general, there are two different types of control loops; open and closed. Open control loops are what the majority of MAV control systems are. There is an FC, that sends a value to the ESC that applies a particular voltage to the motor based on previously calibrated settings. In this method, the final result of the motor spinning is unknown to the flight controller. Therefore given any disturbances, there will be large variances in the response of the overall system. In response to these systems there are smarter, closed loop control. This is the type of control we will focus on. Closed loop systems provide a certain way to measure the output of the rotor based on the input from the FC. This allows for a smarter, more robust system and greater control of the output. \\
	\subsection{Intro to the problem}
	The main problem we address in this paper is determining a type of sensor that can accurately and efficiently measure the output of the propellers in a meaningful way such that a closed control loop can be devised.
	\subsection{Lit review}
	There has been an enormous strive to develop methods to obtain a closed loop control system for MAV's. The methods range from estimation to sensing based on different vectors. The majority of the estimation based controls rely on the voltage or current draw by the motors. Mahoney et al \cite{mahoney1} devised such a system which estimates the thrust using a for loop based calculation of the thrust. This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible. As well their system requires heavy calibration and would not be easily transferable between systems. Similarly Awan et al \cite{awan} developed an adaptive observer based thrust estimation system. This method allowed for the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation. The main issue along this method is that their paper only accounts for hover not flight, as well their models were based around a linearized system and any nonlinear disturbances would cause errors in their system. In contrast Sydney et al \cite{sydney} developed a highly complex system where they modeled the entire system, both linear and nonlinear. By doing so their

	Mahoney et al (2017) have developed an algorithm which bases the control system around an estimation of the thrust from a propeller based on the voltage and current given to the motor by the ESC. Their system works to maintain a thrust given some disturbance. From looking over their algorithm, they have a system which runs through a for loop before detecting an appropriate response to extraneous forces. This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible. As well this method of thrust based control requires a significant amount of calibration for both the propellers and 
	Real-Time Wind Speed Estimation and Compensation for Improved Flight
	Streit developed a control system to compensate for wind disturbances using a pitot-tube sensor coupled with the GPS sensor along with an accompanying estimation algorithm. While this seems similar to the Yeo et al paper, there are some major differences. Streit has only one pitot sensor onboard the UAV which is uni-directional and therefore only applies to forward motion. As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV's as it will be too heavy. 
	Onboard Flow Sensing for Downwash Detection and Avoidance with a Small Quadrotor Helicopter
	Yeo et al have developed a system similar to our proposed idea by fabricating pitot tubes to sit below each propeller and measure the rotor downwash and compare them to the estimated expected wind speed. Their system is ultimately used to localize external noise from other UAV's and therefore an exceedingly accurate measurement is not as important. While the sensor can accurately measure wind speed accurately during vertical motion, there is significant divergence from the ground speed measurement during lateral movement. As well there is a very limited range of speeds that are available for measurement from the probe. 
	\subsection{Scope and application}
	The scope of this paper is to introduce a hot wire anemometer, or wind sensor, as viable option for an external sensor and develop the relationship between the downwash rotor wind speed and the thrust vector of the propeller. With the addition of the sensor, we generate a control system based around the measurements of the wind sensor, using a kalman filter and a simple PI controller. This allows the system to be more robust towards external disturbances such as wind gusts and also more tolerant to internal errors. One other application of the wind sensor is to have an onboard fault detection system, which is in contrast to the majority of prior research, where the fault detection is more of an estimation. The applications for the sensor we introduce can be in any field where MAV's are prevalent, such as filmography, racing, and any other area that requires, agile and reliable control. 
	\section{2}
	\subsection{Wind sensor math/theory}
	We have to start by defining the three different velocities that apply to a propeller.\\
	\begin{eqnarray}
	\label{e1}
	v_x , v_y , v_z \\
	\label{e2}
	v^s_{x} , v^s_{y} , v^s_{z} \\
	\label{e3}
	v^i_{x} , v^i_{y} , v^i_{z}
	\end{eqnarray}
	Where \ref{e1} Is the velocity of the drone, the body frame velocity, \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and \ref{e3} is the induced velocity of the propellers.\\
	Since we are doing only the static tests in this paper, we can disregard the horizontal components of the wind as well as the body frame velocities. Then we can state 
	\begin{eqnarray}
	\nonumber
	v_s = v^s_{z}\\
	\nonumber
	v_i = v^i_{z}
	\end{eqnarray}
	As well, since we have stationary system, the frame velocities can be ignored as well. What the wind sensor will notice is 

@@

	v_{tot} = v_{i} + v_{s}
	\label{vtot}

@@

	Generally, when no disturbances are applied we can assume that $v_s$ is $0$ as a means of simplifying our system.
	Modern Device \cite{md} gives us the equation 
	\begin{eqnarray}
		WS = \frac{(V - V_{z})*0.087288}{3.038517 * T_{c} ^{0.115157}} ^ {3.009364}
		\label{wind_speed}
	\end{eqnarray}
	Where $WS$ is the wind speed,in miles/hour, $V$ is the measured voltage, $V$ is the calibrated voltage when there is no wind, and $T_c$ is the current temperature in celsius which is also measured by the sensor. While the basis of this paper is around the wind speed, it is not important to know the exact wind speed and therefore throughout the rest of our calculations, we only consider the measured voltage. 
	%How does wind speed relate to voltage
	To explain the relation of wind to thrust, let's radically simplify it and assume it is a linear system.  With this being the case, it can be stated that 

@@

	F_p= \frac{\partial p}{\partial t}
	\label{fvm}

@@

	where $F_p$ is the force the propeller exerts, $p$ is momentum and $t$ is time. From this we can expand this to 
	\begin{eqnarray}
	F_p= \frac{mv_{tot} - mv_{s}}{\Delta t}\\ 
	\label{fvm2}
	F_p= m*(v_{tot}-v{s}) 
	\label{fvm3}
	\end{eqnarray}
	where $m$ is the mass of air flowing. Then making the assumption that $\Delta t = 1$ we get \ref{fvm3}.	Now to consider the efficiency of the propeller we can say 
	\begin{eqnarray}	
	v_{i}\prime = v_{i}* \gamma\\
	v_{tot}\prime = v_i\prime + v_s
	\label{eff}
	\end{eqnarray}
	where $\gamma$ is some efficiency factor where $0 \leq  \gamma \leq 1$ which degrades as the stream velocity $v_s$ approaches $v_i$\cite{someone}. In doing so we can assume that for a non-zero $v_s$ 
	F_p\prime < F_p
	This is the reasoning behind why as winds buffet a drone mid-flight, the drone's thrust vector tends to drop. Hence we can measure this change in thrust and correct for it.
	\subsection{Kalman Math}
	\subsection{2.3}
	\subsection{2.4}

@@

	\subsection{Thrust stand}

@@

	\subsection{Wind Sensor Intro}

@@

	\subsection{Wind Sensor Proof}

@@

	We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value. the primary value is from the wind sensor which is measured through an Arduino. The voltage value that the arduino measures is then converted to a thrust value through the power function
	\begin{equation}
	Thrust = 4.701 * 10^{15} * V_w^{6.146} + 0.0731
	\label{wind_power}
	\end{equation}
	The secondary measurement of thrust is a polynomial function that converts the output PWM value that is used to control the propeller. \newline
	\begin{eqnarray}
	Thrust = 1.957*10^{-5}*PWM^4 \\
	- 7.476*10^{-4}*PWM^3 \nonumber\\ 
	+ 1.272*10^{-2}*PWM^2 \nonumber\\
	+ .01092*PWM - .01842 \nonumber
	\label{pwm_poly}
	\end{eqnarray}
	These values are then passed through a Kalman Filter weighted towards the wind sensor. This method allows for the system to accurately determine the thrust value output while reducing noise due to the nature of the wind. Next this value is passed to a PI controller which generates the appropriate response for the error between desired and measured. 
	\subsection{The tests}
	To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response. The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust. As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely. This result gives us the confidence to setup the PI based on the kalman filter's value. 
	To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system. The first step was to create an external disturbance by placing another propeller and blowing wind perpendicular to the axis of the main propeller. This would be akin to horizontal crosswind flow across the propeller.
	\begin{figure}
		\label{content...}
	\end{figure}
	 Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through
	\begin{figure}
		content...
	\end{figure}
	\subsection{Shortcomings and limitations}
	As mentioned previously, having a closed loop system allows for a more robust and agile system which allows for better flight performance. Some of the application for this level of performance include a better landing algorithm, proximity detection of other MAV's, more sophisticated hovering control, fault detection, and fault tolerance. These areas would all benefit by having a physical measurement of the thrust rather than an estimation.

@@

	\subsection{}
	\subsection{5.4}
		\begin{figure}[b]
		\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
		\caption{Block Diagram}
		\label{block_diagram}
	\end{figure}
	\begin{thebibliography}{99}
		\bibitem{mahoney1} Mahoney 2012
		\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
		\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
		\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471 
		\bibitem{awan} A. U. Awan, J. Park and H. J. Kim, "Thrust estimation of quadrotor UAV using adaptive observer," 2011 11th International Conference on Control, Automation and Systems, Gyeonggi-do, 2011, pp. 131-136.
		\bibitem{sydney} N. Sydney, B. Smyth and D. A. Paley, "Dynamic control of autonomous quadrotor flight in an estimated wind field," 52nd IEEE Conference on Decision and Control, Florence, 2013, pp. 3609-3616.
		doi: 10.1109/CDC.2013.6760438

	\end{thebibliography}

\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Real-time Thrust Estimation and Regulation for Multirotor Aerial Vehicle\\
{}
\thanks{}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Adithya Ravishankara}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Bara Emran}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Sherman}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Homayoun Najjaran}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}

@@

\maketitle

\begin{abstract}
In this paper, we present a real-time approach to sense and regulate the thrust produced by rotors with fixed-pitch blade commonly used on multirotor aerial vehicles (MAV). The proposed schemes consist of integrating a wind sensor mounted onboard to measure the wind speed generated by the rotor directly. The wind measurement is then used with a simple control system and effective estimation algorithms to perform a precise controlling of the rotor thrust in real time. This integration significantly improves the disturbance rejection and fault estimation of the thrust and rotor, respectively. Specifically, a direct regulation of the thrust will improve the MAV systems performance while performing aggressive maneuvers or when subjected to external disturbances. Moreover, this approach can be employed to estimate the effective loss of a rotor for fault-tolerant control systems. The features of the proposed approach are demonstrated using a testbed and compared to a classical electrical speed control. Different experiments were performed to validate the efficiency of the proposed approach in maintaining the thrust in the presence of a wind gust and rotor efficiency loss.
\end{abstract}

\begin{IEEEkeywords}
Sensor,Control,Kalman,Quadrotor
\end{IEEEkeywords}

\section{Introduction}
Unmanned aerial vehicles (UAV), especially multirotor, have become quite commonplace in many industries ranging from inspection, racing to military applications \cite{bara}, \cite{Mathe}. Over the past decade, there has been an incredible amount of research and advancement within this field leading to its proliferation and allowing for the technology to become more accessible. One of the major areas of research regarding UAV is the control system that directs the motor-rotor system. The control mechanism ranges in complexity from the common motor-rotor control to a more complex system that takes into consideration parameters such as thrust or torque. The control of the motor-rotor has to account for different external and internal factors, such as the ambient wind speed, the rotation speed of the propeller (RPM), the pitch of the propeller and the internal loops of the Electronic Speed Controller (ESC). Typically, rotor control systems in UAV are operated in open control loops. That is, the flight controller (FC) sends the desired speed value to the ESC that applies a particular voltage to the motor based on previously calibrated settings. The ESC uses the feedback signals of the rotor’s current and voltage to maintain its desired speed. In this method, however, the thrust generated by the propeller spinning is unknown to the FC. Recently, advanced FC employs static aerodynamic models relating rotor speed to estimate and control the generated thrust. Usually, these models are obtained after intensive experiments performed in static-free air environment to detrain the motor’s and propeller’s characteristics. However, when the system is subjected to a disturbance, these models become inaccurate. These external disturbances could accrue due to wind or when the vehicle is performing an agile maneuver. Thus, the lack of a direct measurement of the actual thrust is attracting the interest of the robot community recently. In this paper, we focus on determining a type of sensor that can efficiently measure the generated thrust of a propeller to use it for controlling the UAV. This allows for a smarter and more robust control system.

There has been an enormous strive to develop methods to obtain a closed loop control system for UAVs. The methods range from thrust modeling to estimation using different sensors. The majority of the estimation-based controls rely on the voltage or current drawn by the motors.
Awan et. al. \cite{awan} developed an adaptive observer-based thrust estimation system. This method allowed the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation. However, their proposed structure only accounts for hovering condition and the models were based around a linearized system. As a result, the system was highly violable for disturbances. This was accounted in Sydney et. al. \cite{sydney}, where they have proposed a highly complex estimation system and considered the nonlinear model of the system. Similarly, Mahoney et. al. \cite{mahoney1} devised a system which estimates the thrust using an iterative based calculation. This system while it allows for a valid estimation of the thrust, it is relatively complex and requires heavy computation. Letter in Mahony (2017), they have improved the estimation algorithm using the feedback signal of the voltage and current given to the motor by the ESC. Their system works to maintain a thrust given some disturbance. Still, their system runs through an iterative loop before detecting an appropriate response to extraneous forces. This system while it allows for a robust estimation of the thrust, it is still a complex system. As well their method requires a significant amount of calibration for both the propellers and rotors which makes it harder to employ in different systems. Streit \cite{str} developed a control system to compensate for wind disturbances using a pitot-tube sensor along with an accompanying estimation algorithm. While this seems similar to the Yeo et al paper, there are some major differences. Streit has only one pitot sensor onboard the UAV which is unidirectional and therefore only applies to forward motion. As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV’s as it will be too heavy. Yeo et al have used fabricated pitot tubes placed below each propeller to measure the rotor downwash and compare them to the estimated expected wind speed. Their system is ultimately used to localize external noise from other UAV’s and therefore an exceedingly accurate measurement is not as important. While the sensor can accurately measure wind speed accurately during vertical motion, there is a significant divergence from the ground speed measurement during lateral movement. As well there is a very limited range of speeds that are available for measurement from the probe.

\section{2}
\subsection{Wind sensor math/theory}
We have to start by defining the three different velocities that apply to a propeller.\\
\begin{eqnarray}
\label{e1}
v_x , v_y , v_z \\
\label{e2}
v^s_{x} , v^s_{y} , v^s_{z} \\
\label{e3}
v^i_{x} , v^i_{y} , v^i_{z}
\end{eqnarray}
Where \ref{e1} Is the velocity of the drone, the body frame velocity, \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and \ref{e3} is the induced velocity of the propellers.\\
Since we are doing only the static tests in this paper, we can disregard the horizontal components of the wind as well as the body frame velocities. Then we can state 
\begin{eqnarray}
\nonumber
v_s = v^s_{z}\\
\nonumber
v_i = v^i_{z}
\end{eqnarray}
As well, since we have stationary system, the frame velocities can be ignored as well. What the wind sensor will notice is 
\begin{equation}
v_{tot} = v_{i} + v_{s}
\label{vtot}
\end{equation}	
Generally, when no disturbances are applied we can assume that $v_s$ is $0$ as a means of simplifying our system.
Modern Device \cite{md} gives us the equation 
\begin{eqnarray}
WS = \frac{(V - V_{z})*0.087288}{3.038517 * T_{c} ^{0.115157}} ^ {3.009364}
\label{wind_speed}
\end{eqnarray}
Where $WS$ is the wind speed,in miles/hour, $V$ is the measured voltage, $V$ is the calibrated voltage when there is no wind, and $T_c$ is the current temperature in celsius which is also measured by the sensor. While the basis of this paper is around the wind speed, it is not important to know the exact wind speed and therefore throughout the rest of our calculations, we only consider the measured voltage. 
%How does wind speed relate to voltage
To explain the relation of wind to thrust, let's radically simplify it and assume it is a linear system.  With this being the case, it can be stated that 
\begin{equation}
F_p= \frac{\partial p}{\partial t}
\label{fvm}
\end{equation}
where $F_p$ is the force the propeller exerts, $p$ is momentum and $t$ is time. From this we can expand this to 
\begin{eqnarray}
F_p= \frac{mv_{tot} - mv_{s}}{\Delta t}\\ 
\label{fvm2}
F_p= m*(v_{tot}-v{s}) 
\label{fvm3}
\end{eqnarray}
where $m$ is the mass of air flowing. Then making the assumption that $\Delta t = 1$ we get \ref{fvm3}.	Now to consider the efficiency of the propeller we can say 
\begin{eqnarray}	
v_{i}\prime = v_{i}* \gamma\\
v_{tot}\prime = v_i\prime + v_s
\label{eff}
\end{eqnarray}
where $\gamma$ is some efficiency factor where $0 \leq  \gamma \leq 1$ which degrades as the stream velocity $v_s$ approaches $v_i$\cite{someone}. In doing so we can assume that for a non-zero $v_s$ 
\begin{equation}
F_p\prime < F_p
\end{equation}
This is the reasoning behind why as winds buffet a drone mid-flight, the drone's thrust vector tends to drop. Hence we can measure this change in thrust and correct for it.
\subsection{Adaptive Fuzzy Kalman Filter }

Accurate a priori information of the measurement and process noise statistical matrices of the state estimator is needed to avoid the divergence of the filter [3], [4]. To resolve the problem of having imperfect a priori information, adapting R and/or Q matrices was introduced using several adaptive estimation techniques [5]–[7]. Among these, the Innovative-based Adaptive Estimation (IAE) and Multiple Model Adaptive Estimation (MMAE) are commonly utilized to adapt the Kalman filter. Incorporating the rules of fuzzy logic to adjust the variances of these matrices has been studied in several research works. The Adaptive Fuzzy Kalman Filter q (AFKF) has been designed to improve the performance of the conventional filter in rejecting the measurement noise and estimating the navigational states accurately [8], [9]. 
The recurrent adjustment process of the variances of the statistical matrices Rk is designed based on an IAE approach. This approach is based on a covariance-matching algorithm which examines the degree of the mismatch DoM between the actual covariance $v_{K+1}$ of the residual with its theoretical value $S_{K+1}$. 

@@

DoM = S_{k+1} - C_{k+1}
\label{dom}

@@

After calculating DoM, a Fuzzy Inference System (FIS) has been tuned to compute the adjustment of the measurement noise matrix $R_{k+1}$ and update the matrix at each cycle of state estimation.

@@

R_{k+1} = R_k +\delta R_{K+1}
\label{rk1}

@@

@@

\subsection{RCBenchmark Thrust Stand Dynamometer}

@@

\subsection{Modern Device Wind Sensor}

@@

@@

We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value. the primary value is from the wind sensor which is measured through an Arduino. The voltage value that the arduino measures is then converted to a thrust value through the power function
\begin{equation}
Thrust = 4.701 * 10^{15} * V_w^{6.146} + 0.0731
\label{wind_power}
\end{equation}
The secondary measurement of thrust is a polynomial function that converts the output PWM value that is used to control the propeller. \newline
\begin{eqnarray}
Thrust = 1.957*10^{-5}*PWM^4 \\
- 7.476*10^{-4}*PWM^3 \nonumber\\ 
+ 1.272*10^{-2}*PWM^2 \nonumber\\
+ .01092*PWM - .01842 \nonumber
\label{pwm_poly}
\end{eqnarray}
These values are then passed through a Kalman Filter weighted towards the wind sensor. This method allows for the system to accurately determine the thrust value output while reducing noise due to the nature of the wind. Next this value is passed to a PI controller which generates the appropriate response for the error between desired and measured. 
\subsection{The tests}
Figures \ref{akf1},\ref{akf2} demonstrate the thrust estimation using the conventional and the adaptive fuzzy state estimation techniques. As can be seen, the proposed AFKF has exhibited better performance in terms of rejecting the noise associated with the measurement compared to the classical KF. Figures \ref{akf1},\ref{akf2} presents the estimation errors of the position states. The AFKF shows lower magnitudes of estimation error compared to these of the KF.

To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response. The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust. As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely. This result gives us the confidence to setup the PI based on the kalman filter's value. 
To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system. The first step was to create an external disturbance by placing another propeller and blowing wind perpendicular to the axis of the main propeller. This would be akin to horizontal crosswind flow across the propeller.

Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through

\subsection{Shortcomings and limitations}
As mentioned previously, having a closed loop system allows for a more robust and agile system which allows for better flight performance. Some of the application for this level of performance include a better landing algorithm, proximity detection of other MAV's, more sophisticated hovering control, fault detection, and fault tolerance. These areas would all benefit by having a physical measurement of the thrust rather than an estimation.

@@

\subsection{}
	\begin{figure}[htbp]
	\includegraphics[width=10cm]{images/block_diagram.png}
	\caption{Block Diagram}
	\label{block_diagram}
	\end{figure}
	\begin{figure}[htbp]
	\includegraphics[width=10cm]{images/figure_1/area_heatmap.jpg}
	\caption{Block Diagram}
	\label{area}
	\end{figure}
	\begin{figure}[htbp]
	\includegraphics[width = 7cm]{images/figure_1/dist_heatmap.jpg}
	\caption{Block Diagram}
	\label{dist}
\end{figure}
	\begin{figure}[htbp]
	\includegraphics[width=10cm]{images/figure_1/orientation.jpg}
	\caption{Block Diagram}
	\label{orientation}
\end{figure}
	\begin{figure}[htbp]
	\includegraphics[width=10cm]{images/figure_1/range.jpg}
	\caption{range}
	\label{range}
\end{figure}
	\begin{figure}[htbp]
	\includegraphics[width=10cm]{images/figure_1/response.jpg}
	\caption{response}
	\label{response}
\end{figure}
%	\begin{figure}[b]
%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
%	\caption{Block Diagram}
%	\label{block_diagram}
%\end{figure}
%	\begin{figure}[b]
%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
%	\caption{Block Diagram}
%	\label{block_diagram}
%\end{figure}
%	\begin{figure}[b]
%	\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
%	\caption{Block Diagram}
%	\label{block_diagram}
%\end{figure}

\subsection{5.4}
\begin{thebibliography}{00}
\bibitem{bara}B. J. Emran, D. D. Tannant, and H. Najjaran, “Low-altitude aerial methane concentration mapping,” Remote Sens., vol. 9, no. 8, 2017.
\bibitem{Mathe} K. Máthé and L. Buşoniu, “Vision and Control for UAVs: A Survey of General Methods andof Inexpensive Platforms for Infrastructure Inspection,” Sensors, vol. 15, no. 7, pp. 14887–14916, 2015.
\bibitem{akf} A.H.Mohamed and K. P. Schwarz, “Adaptive Kalman Filtering for INS/GPS,” J. Geod., vol. 73, no. 4, pp. 193–203, 1999.
\bibitem{fuzzy} P. J. Escamilla-Ambrosio and N. Mort, “Development of a fuzzy logic-based adaptive Kalman filter,” in Control Conference (ECC), 2001 European, 2001, pp. 1768–1773.
\bibitem{sebesta} K. D. Sebesta and N. Boizot, “A real-time adaptive high-gain EKF, applied to a quadcopter inertial navigation system,” IEEE Trans. Ind. Electron., vol. 61, no. 1, pp. 495–503, 2014.
\bibitem{Manki} A. Makni, H. Fourati, and A. Y. Kibangou, “Energy-Aware Adaptive Attitude Estimation under External Acceleration for Pedestrian Navigation,” IEEE/ASME Trans. Mechatronics, vol. 21, no. 3, pp. 1366–1375, 2016.
\bibitem{Lin} C. M. Lin and C. S. Hsueh, “Adaptive EKF-CMAC-based multisensor data fusion for maneuvering target,” IEEE Trans. Instrum. Meas., vol. 62, no. 7, pp. 2058–2066, 2013.
\bibitem{Sharman} M. K. Al-Sharman, M. A. Jaradat, and M. F. Abdel-Hafez, “Intelligent attitude and flapping angles estimation of flybarless helicopters under near-hover conditions,” J. Franklin Inst., 2018.
\bibitem{Emran} M. K. Al-Sharman, B. J. Emran, M. A. Jaradat, H. Najjaran, R. Al-Husari, and Y. Zweiri, “Precision landing using an adaptive fuzzy multi-sensor data fusion architecture,” Appl. Soft Comput. J., vol. 69, 2018.
		\bibitem{mahoney1} Mahoney 2012
\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471 
\bibitem{awan} A. U. Awan, J. Park and H. J. Kim, "Thrust estimation of quadrotor UAV using adaptive observer," 2011 11th International Conference on Control, Automation and Systems, Gyeonggi-do, 2011, pp. 131-136.
\bibitem{sydney} N. Sydney, B. Smyth and D. A. Paley, "Dynamic control of autonomous quadrotor flight in an estimated wind field," 52nd IEEE Conference on Decision and Control, Florence, 2013, pp. 3609-3616.
\end{thebibliography}
\end{document}
